Untitled

### 2024-10-25 analysis/paper/access-ice.qmd
Reverse bias colours

climatologies |> 
  _[model %in% c("S2", which_dataset)] |> 
  dcast(time + xgrid + ygrid ~ model, value.var = "aice") |> 
  setnames(which_dataset, "obs") |> 
  ggplot(aes(xgrid, ygrid)) +
  geom_contour_fill(aes(z = S2 - obs, fill = after_stat(level)), 
                    breaks = AnchorBreaks(binwidth = 0.1, exclude = 0)) +
  scale_fill_divergent_discretised(paste0("Bias with respect to ", labels_models[which_dataset])) +
  geomcoord_antarctica +
  geom_antarctica_fill +
  facet_wrap(~ lubridate::month(time, label = TRUE)) +
  wide_legend +
  tag_facets()
```

>>>>

climatologies |> 
  _[model %in% c("S2", which_dataset)] |> 
  dcast(time + xgrid + ygrid ~ model, value.var = "aice") |> 
  setnames(which_dataset, "obs") |> 
  ggplot(aes(xgrid, ygrid)) +
  geom_contour_fill(aes(z = S2 - obs, fill = after_stat(level)), 
                    breaks = AnchorBreaks(binwidth = 0.1, exclude = 0)) +
  scale_fill_divergent_discretised(paste0("Bias with respect to ",
                                          labels_models[which_dataset]),
                                   low = scales::muted("red"),
                                   high = scales::muted("blue")) +
  geomcoord_antarctica +
  geom_antarctica_fill +
  facet_wrap(~ lubridate::month(time, label = TRUE)) +
  wide_legend +
  tag_facets()
```
